\clearpage
\section{Conclusion}

1. By checking the 10x10x10mm single aggregate model, the feasibility of simulate ASR and DEF expansion in confirmed, by checking the cracking generation and inner stress generation. In small scale around aggregate, by introducing initial strain into interfaces, concrete would expanse as the method assumed.

2. By using the proposed constitutive models, the simulation results of expansion behavior in ASR can be represented. Characteristic map cracking pattern is shown in all cases under different condition, and generate as larger expansion introduced.

3. When keeping all other factors the same, as the total coarse aggregate percentage decrease, the map cracking pattern still present, but is more sparse.

4. When keeping all other factors the same, as the total percentage of reactive coarse aggregate decrease, the map cracking pattern also becomes more sparse.

5. The proposed constitutive models, with non-uniform expansion, can represent the characteristic map cracking pattern of DEF.

6. When only change the ratio of coarse aggregate contained, the behavior does not change much, only when comparing cracked interfaces number numerically it can be noticed that lower coarse aggregate case having more smaller cracks rather can larger cracks compare to higher aggregate cases.

7. When changing the range of intensified expansion zone for DEF, the cracking patterAn also shows some difference, but generally very close in all cases with intensification.

8. Though both ASR and DEF shows characteristic map crack pattern in the surface, the inner cracking condition is very different. More large cracks are happening in the center of ASR damaged cases, while the inner part of the DEF expanded model generally remains unchanged under naked eyes.

\section{References}
 
